Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-08-18 Scripts/Initial_Analysis.Rmd
Produced figure 2 with regional zooms

#### Project's Library
packages <- c(
  "dbemImport",
  "tidyverse",
  "here", # for dbem_import `here()`
  "data.table", #dbem_import `fread()`
  "readxl", # for reading excell files
  "janitor", # for clearing names
  "geosphere", # estimate distances between points `distm()`
  "ggrepel",
  "zoo", # for average mean
  "parallel", # for mclapply,
  "sf", # for mapping
  "st", # for mapping
  "rgdal", #Spatial analysis
  "tools", #Spatial analysis 
  "zeallot", # for Juanito's map
  "gmt", # for estimating distances between points
  "viridis"
)

@@

Paths <- paste(my_path("R",extra_path = "Emergence_2005"),Taxon_List,"_emergence.txt",sep="")

# Clean names to match data
matching_names <- my_path("G","Spatial/SAU", "sau_matching_names.csv", read = T)

@@

# Read proportion results
# prop_results <- PropChange(Taxon_List, links="y") %>% 
  # filter(!is.na(eez_neighbour)) %>% 
  # mutate(per_mid_plot =ifelse(per_mid >= 50, 50,
  #                          ifelse(per_mid <= -50,-50,per_mid)
  #                          ),
  #        per_early_plot =ifelse(per_early >= 50, 50,
  #                          ifelse(per_early <= -50,-50,per_early)
  #                          )
  #        )

@@

prop_results <- my_path("R",name="proportion_change_2005.csv", read=T)

@@

# Load all sp in one table
Eme_Res <- bind_rows(lapply(Paths, fread)) %>% 
  filter(
    n_ens == 10
  ) %>% 
  left_join(Neighbours,
            by = c("eez_name","eez_neighbour")
  ) %>% 
  rename(sf_eez_name=eez_name) %>% 
  left_join(matching_names,
            by=  "sf_eez_name") %>% 
  clean_names()
# warnings() for empty data species

@@

# Load it!
World_eez_sf <- st_read(dsn = path_world,
                    layer =file_path_sans_ext(fnam_world)) %>% 
  rename(eez_name = Name) %>% 
  # st_transform(crs = 4326) %>% # 4326
  st_transform(crs = "+proj=eck4") %>% # for tbular plot
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>% 
  clean_names()

# Call world map from natural earth
World_map <- rnaturalearth::ne_countries(scale = 'small', returnclass = c("sf")) %>% 
  rename(fishing_entity = name_long) %>%
  left_join(matching_names,
            by = "fishing_entity") %>% 
  distinct(fishing_entity,.keep_all = TRUE) %>% 
  st_transform(crs = "+proj=eck4") %>% # for tbular plot

# eez_centroid <- read_csv(paste(data_path,"Spatial/eez_centroids.csv", sep = ""))

@@

# Prepare data from results
Data <- results %>% 
  # get coords for sources
  left_join(eez_centroid,
            by = "eez_name") %>%
  rename(source = eez_name,
         start_lon = longitude,
         start_lat = latitude,
         eez_name=eez_neighbour) %>% 
  # get coords for targets
  left_join(eez_centroid,
            by = "eez_name") %>% 
  rename(target = eez_name,
         end_lon = longitude,
         end_lat = latitude) %>% 
  ungroup() %>% 
  # Plot miscs
  mutate(
    per_early = ifelse(is.na(per_early_plot),0,per_early_plot),
    per_mid = ifelse(is.na(per_mid_plot),0,per_mid_plot)
  ) %>% 
  drop_na() %>%
  filter(
    variable == "mean_eez"#,
    # source %in% c("Brazil","Argentina","Chile","Peru","Uruguay")
  )

# Convert to data to spatial
network_data_sf <- Data %>%
  select(start_lon, start_lat, end_lon, end_lat) %>% 
  purrr::transpose() %>% 
  purrr::map(~ matrix(flatten_dbl(.), nrow = 2, byrow = TRUE)) %>% 
  purrr::map(st_linestring) %>%
  st_sfc(crs = 4326) %>%
  st_sf(geometry = .)%>%
  bind_cols(Data) %>%
  select(everything(), geometry) %>% 
  # Set circles ('cus the world is not flat!)
  st_segmentize(units::set_units(100, km)) %>% 
  mutate(geometry = (geometry + c(180,90)) %% c(360) - c(180,90)) %>% 
  st_wrap_dateline(options = c("WRAPDATELINE=YES",  "DATELINEOFFSET=180"), quiet = TRUE) %>% 
  sf::st_sf(crs = 4326)

@@

x <- ggplot() +
  geom_sf(data = subset(World_map, sovereignt != "Antarctica"), size = 0.1, fill = "gray90", col = "gray90") +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray70") +
  geom_point(data = subset(Data, time_step == time & per_chng < 0),
             aes(start_lon,
                 start_lat,
                 col = per_chng),
             size = 0.05,
             col = "gray30",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(paths, time_step == time & per_chng > 0),
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = per_chng
            ),
            size = 0.3,
            arrow = arrow(length = unit(0.009, "npc"),
                          ends = "first"),
            show.legend = NA) +
  my_ggtheme_m() +
  scale_colour_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Data$per_chng)),
    breaks = seq(0,max(Data$per_chng),5),
    # option="magma",
    direction = -1
  ) +
  ggsave("./Figures/figure_connections_early_n50.png",
         width = 10,
         height = 6,
         units = "in"
  )

>>>>

#### Project's Library
packages <- c(
  "dbemImport",
  "tidyverse",
  "here", # for dbem_import `here()`
  "data.table", #dbem_import `fread()`
  "readxl", # for reading excell files
  "janitor", # for clearing names
  "geosphere", # estimate distances between points `distm()`
  "ggrepel",
  "zoo", # for average mean
  "parallel", # for mclapply,
  "sf", # for mapping
  "st", # for mapping
  "rgdal", #Spatial analysis
  "tools", #Spatial analysis 
  "zeallot", # for Juanito's map
  "gmt", # for estimating distances between points
  "viridis",
  "cowplot"
)

@@

# Paths <- paste(my_path("R",extra_path = "Emergence_2005"),Taxon_List_emer,"_emergence.txt",sep="")

# Clean names to match data
Matching_names <- my_path("G","Spatial/SAU", "matching_names.csv", read = T)

@@

# Read proportion results
# prop_results <- PropChange(Taxon_List_emer, links="y") %>% 
  # filter(!is.na(eez_neighbour)) %>% 
  # mutate(per_mid_plot =ifelse(per_mid >= 50, 50,
  #                          ifelse(per_mid <= -50,-50,per_mid)
  #                          ),
  #        per_early_plot =ifelse(per_early >= 50, 50,
  #                          ifelse(per_early <= -50,-50,per_early)
  #                          )
  #        )

@@

Prop_results <- my_path("R",name="proportion_change_2005.csv", read=T)

@@

# Load all sp in one table
Eme_Res <- bind_rows(lapply(Paths, fread)) %>% 
  filter(
    n_ens == 10
  ) %>% 
  left_join(Neighbours,
            by = c("eez_name","eez_neighbour")
  ) %>% 
  rename(sf_eez_name=eez_name) %>% 
  left_join(Matching_names,
            by=  "sf_eez_name") %>% 
  clean_names()

# warnings() for empty data species

@@

# Load it!
World_eez_sf <- st_read(dsn = path_world,
                        layer =file_path_sans_ext(fnam_world)) %>% 
  rename(eez_name = Name) %>% 
  st_transform(crs = 4326) %>% # 4326
  # st_transform(crs = "+proj=eck4") %>% # for tbular plot
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>% 
  clean_names()

# Call world map from natural earth

World_map_dat <- Matching_names %>% 
  group_by(sau_fishing_entity,fishing_entity_id,iso_a3) %>% 
  summarise(n=n()) %>% 
  select(-n)

World_map <- rnaturalearth::ne_countries(scale = 'small', returnclass = c("sf")) %>%
  # st_transform(crs = "+proj=eck4") %>%
  st_transform(crs = 4326) %>% # 4326
  left_join(World_map_dat,
            by = "iso_a3")

# Load eez_centroid data
Eez_centroid <- my_path("D", "Spatial","eez_centroids.csv",read = T)

# Tranform to tubular
Eez_centroid_sf <-st_as_sf(Eez_centroid,
            coords = c("longitude", "latitude")
            ) %>% 
  st_set_crs(4326) #%>% # to match shapefiles
  # st_transform(crs = "+proj=eck4")

# Transform sf to df
Eez_centroid_eck <- as.data.frame(Eez_centroid_sf)

Eez_centroid_eck <- do.call(rbind, st_geometry(Eez_centroid_sf)) %>% 
  as_tibble() %>% 
  setNames(c("lon","lat")) %>% 
  bind_cols(Eez_centroid) %>% 
  select(eez_name,longitude = lon,latitude = lat)

@@

# Prepare data from results
Data <- Prop_results %>% 
  # get coords for sources
  left_join(Eez_centroid_eck,
            by = "eez_name") %>%
  rename(source = eez_name,
         start_lon = longitude,
         start_lat = latitude,
         eez_name=eez_neighbour) %>% 
  # get coords for targets
  left_join(Eez_centroid_eck,
            by = "eez_name") %>% 
  rename(target = eez_name,
         end_lon = longitude,
         end_lat = latitude) %>% 
  ungroup() %>% 
  # Plot miscs
  mutate(
    per_early = ifelse(is.na(per_early_plot),0,per_early_plot),
    per_mid = ifelse(is.na(per_mid_plot),0,per_mid_plot)
  ) %>% 
  drop_na() %>%
  filter(
    variable == "mean_eez"#,
    # source %in% c("Brazil","Argentina","Chile","Peru","Uruguay")
  )

# Convert to data to spatial
network_data_sf <- Data %>%
  select(start_lon, start_lat, end_lon, end_lat) %>% 
  purrr::transpose() %>% 
  purrr::map(~ matrix(flatten_dbl(.), nrow = 2, byrow = TRUE)) %>% 
  purrr::map(st_linestring) %>%
  # st_sfc(crs = 4326) %>%
  st_sfc(crs = "+proj=eck4") %>% # for tbular plot
  st_sf(geometry = .)%>%
  bind_cols(Data) %>%
  select(everything(), geometry) %>% 
  # Set circles ('cus the world is not flat!)
  st_segmentize(units::set_units(100, km)) %>% 
  mutate(geometry = (geometry + c(180,90)) %% c(360) - c(180,90)) %>%
  # mutate(geometry = (geometry + c(18000000,9000000)) %% c(360) - c(18000000,9000000)) %>%
  st_wrap_dateline(options = c("WRAPDATELINE=YES",  "DATELINEOFFSET=180"), quiet = TRUE) %>%
  st_wrap_dateline(options = c("WRAPDATELINE=YES"), quiet = TRUE) %>%
  # sf::st_sf(crs = 4326)
  sf::st_sf(crs = "+proj=eck4") # for tbular plot

@@

## ------------------- ##
# Global Plot
## ------------------- ##

Prop_map <- ggplot() +
  geom_sf(data = subset(World_map, sovereignt != "Antarctica"), size = 0.1, fill = "gray50", col = "gray50") +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray30") +
  geom_point(data = subset(Data, time_step == time & per_chng < 0),
             aes(start_lon,
                 start_lat,
                 col = per_chng),
             size = 0.05,
             col = "gray30",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(paths, time_step == time & per_chng > 0),
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = per_chng
            ),
            size = 0.3,
            arrow = arrow(length = unit(0.009, "npc"),
                          ends = "first"),
            show.legend = NA) +
  my_ggtheme_m() +
  scale_colour_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Data$per_chng)),
    breaks = seq(0,max(Data$per_chng),5),
    # option="magma",
    # direction = -1
  ) +
  ggsave("./Figures/figure_connections_early_n50.png",
  width = 10,
  height = 6,
  units = "in"
  )

## ------------------- ##
# Regional Plots
## ------------------- ##

Lat_am_land <- World_map %>% 
  filter(region_wb %in% c("Latin America & Caribbean") |
          sau_fishing_entity %in% c("USA","Mexico")
         )

Lat_am_eez <- World_eez_sf %>% 
  rename(sf_eez_name = eez_name) %>% 
  left_join(Matching_names) %>% 
  filter(
    # sau_fishing_entity %in% Lat_am_land$sau_fishing_entity,
         !str_detect(sf_eez_name,"Pacific"),
         !sf_eez_name %in% c("USA (East Coast)","Suriname","Guyana","French Guiana","Bermuda (UK)","Brazil","El Salvador")
         )

Lat_am_eez %>% filter(str_detect(sf_eez_name,"Tri"))

Lat_am_data <- Data %>% 
  filter(source %in% Lat_am_eez$sf_eez_name)

Lat_am_paths <- paths %>% 
  filter(source %in% Lat_am_eez$sf_eez_name,
         target %in% Lat_am_eez$sf_eez_name)

Lat_am_map <- ggplot() +
  geom_sf(data = Lat_am_eez, size = 0.1, fill = "white", col = "gray30") +
  geom_sf(data = Lat_am_land, size = 0.1, fill = "gray50", col = "gray40") +
  geom_point(data = subset(Lat_am_data, time_step == time & per_chng < 0 ),
             aes(start_lon,
                 start_lat,
                 col = per_chng),
             size = 1,
             col = "gray30",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(Lat_am_paths, time_step == time & per_chng > 0),
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = per_chng
            ),
            size = 1,
            arrow = arrow(length = unit(0.05, "npc"),
                          ends = "first"),
            show.legend = NA) +
  coord_sf(xlim = c(-100, -55),ylim = c(9, 30)) + 
  labs(x = "Lon", y = "Lat") +
  scale_x_continuous(breaks = seq(-100,60,10)) +
  scale_y_continuous(breaks = seq(10,30,5)) +
  # my_ggtheme_m() +
  theme(legend.position = "",
        panel.background = element_rect(fill = "white")) +
  scale_colour_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Lat_am_data$per_chng)),
    breaks = seq(0,max(Lat_am_data$per_chng),5),
    # option="magma",
    # direction = -1
  );Lat_am_map

## ------------------- ##
# The Med
## ------------------- ##

# Land polygon
Med_land <- World_map %>% 
  filter(region_wb %in% c("Europe & Central Asia","Middle East & North Africa") |
          sau_fishing_entity %in% c("Spain","France")
         )

# EEZ polygon
Med_eez <- World_eez_sf %>% 
  rename(sf_eez_name = eez_name) %>% 
  left_join(Matching_names) %>% 
  filter(sau_fishing_entity %in% Med_land$sau_fishing_entity,
         sf_eez_name != "Spain (Northwest)")

# Med data
Med_data <- Data %>% 
  filter(source %in% Med_eez$sf_eez_name)

# Med paths
Med_paths <- paths %>% 
  filter(source %in% Med_eez$sf_eez_name,
         target %in% Med_eez$sf_eez_name)

# Med plot
Med_map <- ggplot() +
  geom_sf(data = Med_eez, size = 0.5, fill = "white", col = "gray30") +
  geom_sf(data = Med_land, size = 0.5, fill = "gray50", col = "gray40") +
  geom_point(data = subset(Med_data, time_step == time & per_chng < 0 ),
             aes(start_lon,
                 start_lat,
                 col = per_chng),
             size = 1,
             col = "gray30",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(Med_paths, time_step == time & per_chng > 0),
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = per_chng
            ),
            size = 1,
            arrow = arrow(length = unit(0.05, "npc"),
                          ends = "first"),
            show.legend = NA) +
  coord_sf(xlim = c(-3, 35),ylim = c(30, 45)) +
  labs(x = "Lon", y = "Lat") +
  scale_x_continuous(breaks = seq(-5,35,10)) +
  scale_y_continuous(breaks = seq(30,50,5)) +
  # my_ggtheme_m() +
  theme(legend.position = "",
        panel.background = element_rect(fill = "white")) +
  scale_colour_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Med_data$per_chng)),
    breaks = seq(0,max(Med_data$per_chng),5),
    # option="magma",
    # direction = -1
  );Med_map

## ------------------- ##
# Northern Europe
## ------------------- ##

Eu_land <- World_map %>% 
  filter(
    continent == "Europe",
    sau_fishing_entity != "Iceland"
    )

# 
# ggplot(N_Eu_land) +
#   geom_sf()

Eu_eez <- World_eez_sf %>% 
  rename(sf_eez_name = eez_name) %>% 
  left_join(Matching_names) %>% 
  filter(
    !sf_eez_name %in% c("Iceland", "Norway","Italy","Greece","Croatia","Bulgaria","Romania"),
    !str_detect(sf_eez_name,"Spain")
  )

Eu_eez %>% filter(str_detect(sf_eez_name,"Romania"))

Eu_data <- Data %>% 
  filter(source %in% Eu_eez$sf_eez_name)

Eu_paths <- paths %>% 
  filter(source %in% Eu_eez$sf_eez_name,
         target %in% Eu_eez$sf_eez_name)

Eu_map <- ggplot() +
  geom_sf(data = Eu_eez, size = 0.5, fill = "white", col = "gray30") +
  geom_sf(data = Eu_land, size = 0.5, fill = "gray50", col = "gray40") +
  geom_point(data = subset(Med_data, time_step == time & per_chng < 0 ),
             aes(start_lon,
                 start_lat,
                 col = per_chng),
             size = 1,
             col = "gray30",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(Eu_paths, time_step == time & per_chng > 0),
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = per_chng
            ),
            size = 1,
            arrow = arrow(length = unit(0.05, "npc"),
                          ends = "first"),
            show.legend = NA) +
  coord_sf(xlim = c(-15, 30), ylim = c(45, 65)) +
  labs(x = "Lon", y = "Lat") +
  scale_y_continuous(breaks = seq(45,65,10)) +
  # scale_x_continuous(breaks = seq(45,65,10)) +
  # my_ggtheme_m() +
  theme(legend.position = "",
        panel.background = element_rect(fill = "white", color = "white"),
        panel.grid.major =  element_line(color = "white")
        ) +
  scale_colour_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Eu_data$per_chng)),
    breaks = seq(0,max(Eu_data$per_chng),5),
    # option="magma",
    # direction = -1
  );Eu_map

## ------------------- ##
# Final Figure
## ------------------- ##

gc()
plot_all <- ggdraw() +
      # map
      draw_plot(Prop_map, x = 0, y = 0.45, width = 1, height = 0.58) +
      # Lat America reg plor
      draw_plot(Lat_am_map, x = 0.1, y = 0.08, width = 0.3, height = 0.4) +
      # Europe reg plot
      draw_plot(Eu_map, x = 0.35, y = 0.08, width = 0.3, height = 0.4) +
      # Med regional plot
      draw_plot(Med_map, x = 0.65, y = 0.08, width = 0.3, height = 0.4) +
      draw_plot_label(label = c("a", "b"), 
                      size = 20,
                      x = c(0, 0), 
                      y = c(1, 0.45)
      ) #+
      # draw_plot_label(label = c("Revenue (USD) | Catch (Tonnes)","(Million)"), 
                      # size = 8,
                      # x = c(0.325,0.485), 
                      # y = c(0.31,0.29)
      )

    save_plot(
      # paste(Figures_Path,"100_25_Bins_Value_Region.png",sep=""),
      "test.png",
      plot_all,
      base_height = 8,
      base_width = 8
    )
